On the marginal value of swimming in woodland caribou

### 2021-05-25 paper/manuscript.Rmd
P3

Our focus on forage is due to the limited presence of predators in our system. Throughout their range,
wolves (*Canis lupus*) are the primary predator of caribou, although there are no wolves on the Island
of Newfoundland, predation on adult caribou by coyotes (*Canis latrans*) does occur (Lewis and Mahoney
2014). Within the Fogo Island archipelago, coyotes exist at low density (Huang et al. 2021) and the
probability of occurrence decreases on the smaller islands. The low density of predators throughout
the archipelago is therefore an unlikely driver of swimming in our system, though predation may
still influence swimming behaviour for caribou elsewhere in their range (e.g. Jeffery et al. 2007).

>>>>

Our focus on forage is due to the limited presence of predators in our system. Throughout their range, wolves (*Canis lupus*) are the primary predator of caribou. Because there are no wolves on the Island of Newfoundland, coyotes (*Canis latrans*) and black bears (*Ursus americanus*) are the majors predator of caribou (Lewis and Mahoney 2014). Within the Fogo Island archipelago there are no black bears and coyotes exist at low density (Huang et al. 2021), while the probability of coyote occurrence decreases on the smaller islands. The low density of predators throughout the archipelago is therefore an unlikely driver of swimming in our system, though predation may still influence swimming behaviour for caribou elsewhere in their range (e.g. Jeffery et al. 2007).
